Exploring and Validating the Motives Behind API Evolution: A Case Study

### 2015-03-20 rmtw/a6/latex8.tex
title wip

\title{Wu-Tang Clan}

@@

The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of relating documentation. From the source code we extracted information regarding the public facing APIs. Specifically, we collected information about return types, parameters and method names. The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. From the archival documentation we collected information regarding the intent behind the functionality in API calls. For example, we examined differences in descriptions of methods prior to and after return types or parameters were renamed. This information provided insight into the motivation behind the changes.

These collection methods were the most appropriate given that the data were readily available from the company. This did bring with it concerns that the data were not collected for the purpose of research \cite{!!! host}, meaning that some of the data had the risk of being irrelevant and that erroneous data had the potential to exist. Collection from another techniques were required to fill in the missing data.

A first degree interview was also be conducted after the initial source inspections had taken place. The main purpose was to validate our findings with the architects of the API. Furthermore, the interviews provided additional insight into decisions and motivations behind changes that we were unaware of. The interviews also provided us with more insight about the end users of the system. Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.

>>>>

\title{Exploring and Validating the Motives Behind API Evolution: A Case Study}

@@

%Explain that we have two versions of the API, old and new
%Explain about how we'll collect them, i.e. in tables and spreadsheets. Different versions etc
%Double inspection will be performed. Two steps, independently by each of us to reduce research bias and human error.

The data were collected primarily through third degree methods, such as first hand inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of APIs which the company had developed. An older version which is currently released and a newer version which is soon to be deployed. Each version of the API had its own relevant documentation. The documentation provided explanations of the features offered by the API and illustrated some examples of its usage.

From the APIs we collected data about method names, parameters and return types. The data were collected from both versions of the APIs, with the changes between the two versions being of particular interest. From the archival documentation we collected information regarding the motive behind the functionality in API calls. This information provided insight into the motives behind the changes. For example, we examined differences in descriptions of methods prior to and after return types or parameters were renamed.

A double inspection and a single joint inspection were used to collect the information from the APIs and the documentation. This was performed to reduce researcher bias and human error. Once collected, the data were input into tables and spreadsheets according to the API version.

These collection methods were the most appropriate given that the data were readily available from the company. This brought concerns that the data were not collected for the purpose of research \cite{runeson2009guidelines}, meaning there was a risk of data being irrelevant or erroneous.

Collecting data by using other techniques were required to fill in the missing data. First degree interviews were also conducted after the initial source inspections had taken place. The main purpose was to validate our findings with the architects of the API. Furthermore, the interviews provided additional insight into decisions and motivations behind changes that we were unaware of. The interviews also provided us with more insight about the end users of the system. Another added benefit was that we were able to triangulate our results with responses in the interviews, allowing us to validate, or refute our findings.

%why methods apply to our study, why the techniques were used. Motivate relationship between the techniques and the RQs
